Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-09 paper/ijcai16.tex
paper: add a note to the equation, update slightly.

Let $k$ be the set size and $n$ be the number of examples (answers).

@@

\begin{align}
    \max_{M, W, X}
        & \;\; M - \frac{\alpha}{k n} \sum_{i=1}^k \| \veps^{(i)} \|_1 - \frac{\beta}{k} \sum_{i=1}^k \| \vw^{(i)} \|_1 + \frac{\gamma}{k} \sum_{i=1}^k \langle \vw^{(i)}, \vx^{(i)} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{(i)}, \vy^{(h)}_+ - \vy^{(h)}_- \rangle \geq M - \varepsilon^{(i)}_h
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{(i)}, \vx^{(i)} - \vx^{(j)} \rangle \geq M \label{cnst-ws-m}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \leq \vw^{(i)} \leq \vw^\top
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{(i)} \in \calX_{\text{feasible}}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{(i)}_h \geq 0
    \\
        & \;\; M \geq 0
\end{align}

@@

>>>>

Let $k$ be the set size and $n$ be the number of examples (answers). Here
the $\vw$'s are non-negative real vectors, while the $\vx$'s are 0-1
vectors.

@@

\begin{align}
    \max_{M, W, X}
        & \;\; M - \frac{\alpha}{k n} \sum_{i=1}^k \| \veps^{(i)} \|_1 - \frac{\beta}{k} \sum_{i=1}^k \| \vw^{(i)} \|_1 + \frac{\gamma}{k} \sum_{i=1}^k \langle \vw^{(i)}, \vx^{(i)} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{(i)}, \vy^{(h)}_+ - \vy^{(h)}_- \rangle \geq M - \varepsilon^{(i)}_h
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{(i)}, \vx^{(i)} - \vx^{(j)} \rangle \geq M \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \leq \vw^{(i)} \leq \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{(i)} \in \calX_{\text{feasible}}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{(i)}_h \geq 0
    \\
        & \;\; M \geq 0
\end{align}

@@

Note that due to the non-negativity of $\vw^\bot$, Eq.~\ref{eq:wbounds}
subsumes the non-negativity constraint $\forall \; i \in [k] \;.\; \vw^{(i)}$.

\stefano{for $k=1$, setting $\alpha < 1$  renders the problem unbounded, as
Eq.~\ref{eq:wxconstr} vanishes.}
